Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-01 paper/Draft.tex
Revised formatting of figures

	In Figure \ref{Inflationshocks}, all four shocks are plotted in quarterly between 1985-2019. All shocks are normalized by its respective sample standard deviations.

@@

	\begin{figure}[ht]
		\centering
		\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
				\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
					\smallskip
				\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
		\end{subfigure}	
	    \hfill 
	    \begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
	\end{subfigure}
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
		\label{ReplicateCoibionBefore2007}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
		\includegraphics[width=7cm]{figures/Inf_ashocks.png} \\
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
		\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} \\
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} \\
		\smallskip 
		\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
		\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
		\label{ReplicateCoibionwholeperiod}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=4.5cm,height=3.5cm]{figures/CPIAU_ashocks_nmpM.png}  
		\includegraphics[width=9cm,height=3.5cm]{figures/CPIAU_ashocksM.png} \\
		\smallskip
		\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEFE_ashocks_nmpM.png} 
		\includegraphics[width=9cm,height=3.5cm]{figures/SCEFE_ashocksM.png} \\
		\smallskip
		\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEDisg_ab_ashocks_nmpM.png} 
		\includegraphics[width=9cm,height=3.5cm]{figures/SCEDisg_ab_ashocksM.png} \\
		\smallskip 
		\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEVar_ab_ashocks_nmpM.png} 
		\includegraphics[width=9cm,height=3.5cm]{figures/SCEVar_ab_ashocksM.png} 
		\caption{ Responses of Inflation and Household Forecast Moments: 2013-2019}
		\label{SCE_IR}
	\end{figure}

>>>>

	In Figure \ref{Inflationshocks}, all four shocks are plotted in quarterly between 1985-2019 and normalized by its respective sample standard deviations.

@@

\begin{figure}[ht]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Technology and Oil Shocks}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
	\end{subfigure}
	\hspace{1em}
	\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\caption{Monetary Policy Shocks}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
	\end{subfigure}
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
	\label{ReplicateCoibionBefore2007}
\end{figure}

@@

		\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
			\centering
			\caption{Technology and Oil Shocks}
			\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
			\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
			\smallskip 
			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
			\smallskip 
			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
		\end{subfigure}
		\hfill
		\hspace{1em}
		\begin{subfigure}[b]{0.5\textwidth}
			\caption{Monetary Policy Shocks}
			\includegraphics[width=7cm]{figures/Inf_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
		\end{subfigure} 
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
		\label{ReplicateCoibionwholeperiod}
	\end{figure}

@@

	\begin{figure}[ht]

		\begin{subfigure}[b]{0.35\textwidth}
			\centering
			\caption{Technology Shocks}
			\includegraphics[width=4.5cm,height=3.5cm]{figures/CPIAU_ashocks_nmpM.png}
			\smallskip
			\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEFE_ashocks_nmpM.png} 
			\smallskip
			\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEDisg_ab_ashocks_nmpM.png}
			\smallskip
			\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEVar_ab_ashocks_nmpM.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.65\textwidth}
			\centering
			\caption{Monetary Policy Shocks}
			\includegraphics[width=9cm,height=3.5cm]{figures/CPIAU_ashocksM.png} 
			\smallskip
			\includegraphics[width=9cm,height=3.5cm]{figures/SCEFE_ashocksM.png} 
			\smallskip
			\includegraphics[width=9cm,height=3.5cm]{figures/SCEDisg_ab_ashocksM.png} 
			\smallskip 
			\includegraphics[width=9cm,height=3.5cm]{figures/SCEVar_ab_ashocksM.png} 
		\end{subfigure}
		\caption{ Responses of Inflation and Household Forecast Moments: 2013-2019}
		\label{SCE_IR}
	\end{figure}
